AtmoSwing (v1.4): Analog Technique Model for Statistical weather forecastING

### 2015-10-15 AtmoSwing - Geoscientific Model Development/template.tex
Addition of the nomenclature.

\subsection{Its evolution}
\label{sec:method:evolution}

@@

\subsection{References implementations for precipitation forecasting}

@@

%\subsection{R0, les origines}
%\label{sec:etat_art:R0}

%Une référence préliminaire résulte des travaux de \citet{Guilbaud1997} et \citet{Obled2002}. Elle est constituée d'un seul niveau d'analogie sur la circulation atmosphérique considérée à 1000~hPa et 700~hPa (R0a, Table \ref{table:R0a}) ou 500~hPa (R0b, Table \ref{table:R0b}). Le critère S1 de Teweles-Wobus est alors utilisé pour comparer les champs de géopotentiel.

\begin{table}[htbp]
	\caption{R0a.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z700 & 00, 24~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
			& Z1000 & 00, 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:R0a}
\end{table}

\begin{table}[htbp]
	\caption{R0b.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z500 & 00, 24~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
			& Z1000 & 00, 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:R0b}
\end{table}

@@

\begin{table}[htbp]
	\caption{R1.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
			& Z500 & 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:R1}
\end{table}

@@

\begin{table}[htbp]
	\caption{R2.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
			& Z500 & 24~h & & \\ 
			\hline
			2 & TPW * RH850 & 12, 24~h & RMSE & 30 \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:R2}
\end{table}

@@

\begin{table}[htbp]
	\caption{R3a.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{75} \\
			& Z500 & 18~h & & \\ 
			\hline
			2 & TPW * RH925 & 06, 18~h & RMSE & 30 \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:R3a}
\end{table}

\begin{table}[htbp]
	\caption{R3b.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
			& Z 500~hPa & 18~h & & \\ 
			\hline
			2 & V700 * TPW * RH700 & 06, 18~h & RMSE & 25 \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:R3b}
\end{table}

\begin{table}[htbp]
	\caption{R3c.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
			& Z 500~hPa & 18~h & & \\ 
			\hline
			2 & V925 * TPW * RH925 & 06, 18~h & RMSE & 25 \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:R3c}
\end{table}

@@

\begin{table}[htbp]
	\caption{R4a.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline
			\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
			& T600 & 12~h & & \\ 
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
			& Z 500~hPa & 24~h & & \\ 
			\hline
			2 & TPW * RH850 & 12, 24~h & RMSE & 25 \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:R4a}
\end{table}

\begin{table}[htbp]
	\caption{R4b.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline
			\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
			& T600 & 12~h & & \\ 
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
			& Z 500~hPa & 24~h & & \\ 
			\hline
			\multirow{2}{*}{2} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
			& TPW * RH700 & 12, 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:R4b}
\end{table}

\begin{table}[htbp]
	\caption{R4c.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline
			\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
			& T600 & 12~h & & \\ 
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
			& Z 500~hPa & 24~h & & \\ 
			\hline
			\multirow{2}{*}{2} & TPW * RH925 & 06-30~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
			& TPW * RH700 & 06-30~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:R4c}
\end{table}

@@

\begin{table}[htbp]
	\caption{R5a.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline
			\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
			& T600 (1 point) & 12~h & & \\ 
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
			& Z 500~hPa & 24~h & & \\ 
			\hline
			2 & W850 & 06-24~h & RMSE & 70 \\
			\hline
			3 & TPW * RH850 & 12, 24~h & RMSE & 25 \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:R5a}
\end{table}

\begin{table}[htbp]
	\caption{R5b.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline
			\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
			& T600 (1 point) & 12~h & & \\ 
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
			& Z 500~hPa & 24~h & & \\ 
			\hline
			2 & W850 & 06-24~h & RMSE & 70 \\
			\hline
			\multirow{2}{*}{3} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
			& TPW * RH700 & 12, 24~h & & \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:R5b}
\end{table}

@@

\subsection{The classic calibration approach}

@@

\section{The global optimization tools}

>>>>

\subsection{Evolution of the method}
\label{sec:method:evolution}

@@

\subsection{Proposed nomenclature}

Variants of the analogue method parameterization are numerous and it is not always easy to reference them in a short and descriptive way. We thus propose a basic nomenclature (Figure \ref{figure:nomenclature}) in order to give an idea of the structure in a simple identifier. This one cannot describe all the parameters of the method, but quickly illustrate the structure of the implementation. This is particularly useful when working with a global optimization method, where nothing is fixed but the very structure of the method.

\begin{figure}[htbp]
	\includegraphics[width=8.3cm]{figures/nomenclature.pdf}
	\caption{Proposed structure for naming the parameterizations of the analogue method.}
	\label{figure:nomenclature}
\end{figure}

The naming contains different blocs (separated by an hyphen) for the various levels of analogy. It starts with the specification of the preselection (P; can be omitted when comparing methods with the same preselection approaches), which can be nowadays of 2 types:
\begin{itemize}
	\setlength\itemsep{-2px}
	\item C: calendar period ($\pm 60$ days around the target date)
	\item T: based on air temperature \citep{BenDaoud2010}
\end{itemize}

Then, the following levels of analogy are listed. They may start with an optional A (for analogy) when other methods are mixed into the parameterization \citep[see eg. ][]{Chardon2014}. For every level of analogy, we first provide the number of variables used (combination of atmospheric levels and time of observation) and then give the short name of the variable (according eg to ECMWF conventions; in upper case), for example:
\begin{itemize}
	\setlength\itemsep{-2px}
	\item Z : geopotential (circulation)
	\item HI : humidity index (TPW * RH)
	\item HF : humidity flux (V * TPW * RH)
	\item TPW : total precipitable water
	\item V : wind velocity
	\item W : vertical velocity
\end{itemize}

In order to keep the identifier simple, no value of atmospheric level neither time of observation is specified. Moreover, the analogy criterion is not specified and is supposed to be S1 for Z and RMSE for the other variables. If anything changes from these conventions, it can be noted as a flag. The flag (lower case) can also give other information, such as the optimization method:
\begin{itemize}
	\setlength\itemsep{-2px}
	\item cc : classic calibration (can be omitted as considered as default, see section \ref{sec:classic})
	\item go : global optimization (by means of genetic algorithms for example, see section \ref{sec:gas})
\end{itemize}

This nomenclature can be adapted to specific needs, or simplified for a better readability (eg. by removing the specification of the preselection). Examples are provided in the following section.

\subsection{References for precipitation forecasting}

@@

The first parameterization comes from the work of \citet{Guilbaud1997} and \citet{Obled2002}. It consists of a single level of analogy on the atmospheric circulation. The score S1 (Teweles-Wobus, Eq. \ref{eq:S1}) is processed on the geopotential height at 1000~hPa (Z1000) and 700~hPa (Z700) (Table \ref{table:R0a}) or 500~hPa (Z500) (Table \ref{table:R0b}), both at 00~h and 24~h. The number of analogues considered is 50.

\begin{table}[htbp]
	\caption{Method of type PC-4Z proposed by \citep{Guilbaud1997}.}
	\begin{tabular}{ccccc}
		\tophline
		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
		\middlehline
		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
		\middlehline 
		\multirow{2}{*}{1} & Z700 & 00, 24~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
		& Z1000 & 00, 24~h & & \\ 
		\bottomhline 
	\end{tabular} 
	\label{table:R0a}
\end{table}

\begin{table}[htbp]
	\caption{Variant of the PC-4Z method proposed by \citep{Guilbaud1997}.}
	\begin{tabular}{ccccc}
		\tophline
		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
		\middlehline 
		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
		\middlehline 
		\multirow{2}{*}{1} & Z500 & 00, 24~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
		& Z1000 & 00, 24~h & & \\ 
		\bottomhline 
	\end{tabular} 
	\label{table:R0b}
\end{table}

@@

\begin{table}[htbp]
	\caption{Method of type PC-2Z proposed by \citep{Bontron2004}.}
	\begin{tabular}{ccccc}
		\tophline
		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
		\middlehline 
		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
		\middlehline 
		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
		& Z500 & 24~h & & \\ 
		\bottomhline 
	\end{tabular} 
	\label{table:R1}
\end{table}

@@

\begin{table}[htbp]
	\caption{Method of type PC-2Z-2HI proposed by \citep{Bontron2004}.}
	\begin{tabular}{ccccc}
		\tophline
		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
		\middlehline 
		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
		\middlehline 
		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
		& Z500 & 24~h & & \\ 
		\middlehline
		2 & TPW * RH850 & 12, 24~h & RMSE & 30 \\
		\bottomhline 
	\end{tabular} 
	\label{table:R2}
\end{table}

@@

\begin{table}[htbp]
	\caption{Method of type PC-2Z-2HI proposed by \citep{Marty2010}.}
	\begin{tabular}{ccccc}
		\tophline
		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
		\middlehline 
		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
		\middlehline 
		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{75} \\
		& Z500 & 18~h & & \\ 
		\middlehline
		2 & TPW * RH925 & 06, 18~h & RMSE & 30 \\
		\bottomhline 
	\end{tabular} 
	\label{table:R3a}
\end{table}

\begin{table}[htbp]
	\caption{Method of type PC-2Z-2HF proposed by \citep{Marty2010}.}
	\begin{tabular}{ccccc}
		\tophline
		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
		\middlehline 
		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
		\middlehline 
		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
		& Z 500~hPa & 18~h & & \\ 
		\middlehline
		2 & V700 * TPW * RH700 & 06, 18~h & RMSE & 25 \\
		\bottomhline 
	\end{tabular} 
	\label{table:R3b}
\end{table}

\begin{table}[htbp]
	\caption{Method of type PC-2Z-2HF proposed by \citep{Marty2010}.}
	\begin{tabular}{ccccc}
		\tophline
		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
		\middlehline 
		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
		\middlehline 
		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
		& Z 500~hPa & 18~h & & \\ 
		\middlehline
		2 & V925 * TPW * RH925 & 06, 18~h & RMSE & 25 \\
		\bottomhline 
	\end{tabular} 
	\label{table:R3c}
\end{table}

@@

\begin{table}[htbp]
	\caption{Method of type P2T-2Z-2HI proposed by \citep{BenDaoud2010}.}
	\begin{tabular}{ccccc}
		\tophline
		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
		\middlehline
		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
		& T600 & 12~h & & \\ 
		\middlehline 
		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
		& Z 500~hPa & 24~h & & \\ 
		\middlehline
		2 & TPW * RH850 & 12, 24~h & RMSE & 25 \\
		\bottomhline 
	\end{tabular} 
	\label{table:R4a}
\end{table}

\begin{table}[htbp]
	\caption{Method of type P2T-2Z-4HI proposed by \citep{BenDaoud2010}.}
	\begin{tabular}{ccccc}
		\tophline
		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
		\middlehline
		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
		& T600 & 12~h & & \\ 
		\middlehline 
		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
		& Z 500~hPa & 24~h & & \\ 
		\middlehline
		\multirow{2}{*}{2} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
		& TPW * RH700 & 12, 24~h & & \\ 
		\bottomhline 
	\end{tabular} 
	\label{table:R4b}
\end{table}

\begin{table}[htbp]
	\caption{Method of type P2T-2Z-10HI proposed by \citep{BenDaoud2010}.}
	\begin{tabular}{ccccc}
		\tophline
		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
		\middlehline
		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
		& T600 & 12~h & & \\ 
		\middlehline 
		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
		& Z 500~hPa & 24~h & & \\ 
		\middlehline
		\multirow{2}{*}{2} & TPW * RH925 & 06-30~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
		& TPW * RH700 & 06-30~h & & \\ 
		\bottomhline 
	\end{tabular} 
	\label{table:R4c}
\end{table}

@@

\begin{table}[htbp]
	\caption{Method of type P2T-2Z-4W-2HI proposed by \citep{BenDaoud2010}.}
	\begin{tabular}{ccccc}
		\tophline
		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
		\middlehline
		\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
		& T600 (1 point) & 12~h & & \\ 
		\middlehline 
		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
		& Z 500~hPa & 24~h & & \\ 
		\middlehline
		2 & W850 & 06-24~h & RMSE & 70 \\
		\middlehline
		3 & TPW * RH850 & 12, 24~h & RMSE & 25 \\
		\bottomhline 
	\end{tabular} 
	\label{table:R5a}
\end{table}

\begin{table}[htbp]
	\caption{Method of type P2T-2Z-4W-4HI proposed by \citep{BenDaoud2010}.}
	\begin{tabular}{ccccc}
		\tophline
		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
		\middlehline
		\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
		& T600 (1 point) & 12~h & & \\ 
		\middlehline 
		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
		& Z 500~hPa & 24~h & & \\ 
		\middlehline
		2 & W850 & 06-24~h & RMSE & 70 \\
		\middlehline
		\multirow{2}{*}{3} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
		& TPW * RH700 & 12, 24~h & & \\
		\bottomhline 
	\end{tabular}
	\label{table:R5b}
\end{table}

\begin{table}[htbp]
	\caption{Method of type PC-4Zo proposed by \citep{Horton2012}.}
	\begin{tabular}{ccccc}

	\end{tabular}
	\label{table:R6a}
\end{table}

\begin{table}[htbp]
	\caption{Method of type PC-4Zo-2HIo proposed by \citep{Horton2012}.}
	\begin{tabular}{ccccc}

	\end{tabular}
	\label{table:R6b}
\end{table}

@@

\subsection{The classic calibration approach}
\label{sec:classic}

@@

\section{The global optimization tools}
\label{sec:gas}
